An open reproducible framework for the study of the iterated prisoner's dilemma

### 2015-10-16 tex/paper.tex
Minor tidying.

This library is motivated by an ongoing discussion in the academic community
about reproducible research \cite{Crick2014a, Prlic2012, Sandve2013,
Hong2015a}. The library is:

@@

The library is written in Python (\url{http://www.python.org/}) which is a
popular language in the academic community with libraries developed for:

\begin{itemize}
    \item Machine learning (\url{http://scikit-learn.org/});
    \item Visualisation (\url{http://matplotlib.org/});
    \item Mathematics (\url{http://www.sagemath.org/}).
\end{itemize}

In \cite{Isaac2008} Python is described as an appropriate language for the
reproduction of Iterated Prisoner's dilemma tournaments due to it's object
oriented nature and readability.

The library itself is available at
\url{https://github.com/Axelrod-Python/Axelrod}. This is a hosted git repository
which. Git is a popular version control system which is one of the recommended
aspects of reproducible research \cite{Crick2014a, Sandve2013}.

Figure~\ref{fig:demo_tournament_commands} shows a very simple example of using
the library to create a basic tournament with the graphical output shown in
Figure~\ref{fig:demo_tournament}.

@@

    def test_strategy(self):
        """
        If opponent defects at any point then the player will defect forever
        """
        self.responses_test([C, D, D, D], [C, C, C, C], [C])
        self.responses_test([C, C, D, D, D], [C, D, C, C, C], [D])
    \end{lstlisting}
    \caption{Source code for the Grudger strategy.}
    \label{fig:grudger}
\end{figure}

>>>>

This library is motivated by an ongoing discussion in the academic community
about reproducible research \cite{Crick2014a, Hong2015a, Prlic2012, Sandve2013},
and is:

@@

The library is written in Python (\url{http://www.python.org/}) which is a
popular language in the academic community with libraries developed for a
variety of uses including:

\begin{itemize}
    \item Machine learning (\url{http://scikit-learn.org/});
    \item Visualisation (\url{http://matplotlib.org/});
    \item Mathematics (\url{http://www.sagemath.org/});
    \item Astrophysics (\url{http://www.astropy.org/});
    \item Data manipulation (\url{http://pandas.pydata.org/});
    \item Algorithmic Game Theory (\url{http://gambit.sourceforge.net/)}).
\end{itemize}

Furthermore \cite{Isaac2008} Python is described as an appropriate language for the
reproduction of Iterated Prisoner's dilemma tournaments due to it's object
oriented nature and readability.

The library itself is available at
\url{https://github.com/Axelrod-Python/Axelrod}. This is a hosted git
repository. Git is a popular version control system which is one of the
recommended aspects of reproducible research \cite{Crick2014a, Sandve2013}.

Installation of the library is straightforward as it is available via the
standard Python installation package: `pip'
(\url{https://pypi.python.org/pypi}). This ensures it can be used on all major
operating systems (Windows, OS X and Linux).

Figure~\ref{fig:demo_tournament_commands} shows a very simple example of using
the library to create a basic tournament giving the graphical output shown in
Figure~\ref{fig:demo_tournament}.

@@

    def test_strategy(self):
        """
        If opponent defects at any point then the player will defect forever
        """
        self.responses_test([C, D, D, D], [C, C, C, C], [C])
        self.responses_test([C, C, D, D, D], [C, D, C, C, C], [D])
    \end{lstlisting}
    \caption{Test code for the Grudger strategy.}
    \label{fig:grudger_test}
\end{figure}
